\subsection{Analysis of Vandalism Classifiers}

%%{{{ FIGURE:ROCPOINTS
\begin{figure*}[htp]
\centering
\begin{tikzpicture}
	\pgfplotsset{
		xtick distance=0.1,
		ytick distance=0.1,
	}
	\begin{axis}[
		xlabel=$FPR$,
		ylabel=$TPR$,
		legend columns=3,
		legend entries={
			RF,
			RF-SMOTE,
			RF-LNSMOTE,
			CRF-200-1,
			CRF-200-1-SMOTE,
			CRF-200-1-LNSMOTE,
			CRF-100-2,
			CRF-100-2-SMOTE,
			CRF-100-2-LNSMOTE,
			CRF-50-4,
			CRF-50-4-SMOTE,
			CRF-50-4-LNSMOTE,
		},
		legend to name=class_legend
	]
		\addplot[
			scatter,
			only marks,
			point meta=explicit symbolic,
			every mark/.append style={
				/tikz/mark size=3pt
			},
			scatter/classes={
				rf-noresampling={
					mark=text,
					text mark=$\Box$
				},
				rf-smote={
					mark=text,
					text mark=$\boxplus$
				},
				rf-lnsmote={
					mark=text,
					text mark=$\boxtimes$
				},
				crf-200-1={
					mark=text,
					text mark=$\triangle$
				},
				crf-200-1-smote={
					mark=text,
					text mark=$\triangleleft$
				},
				crf-200-1-lnsmote={
					mark=text,
					text mark=$\triangleright$
				},
				crf-100-2={
					mark=text,
					text mark=$\medcircle$
				},
				crf-100-2-smote={
					mark=text,
					text mark=$\oplus$
				},
				crf-100-2-lnsmote={
					mark=text,
					text mark=$\otimes$
				},
				crf-50-4={
					mark=text,
					text mark=$\Diamond$
				},
				crf-50-4-smote={
					mark=text,
					text mark=$\diamondplus$
				},
				crf-50-4-lnsmote={
					mark=text,
					text mark=$\diamondtimes$
				}
			},
		]
		table[
			x={FPR},
			y={TPR},
			meta=klasifikasi,
		]
		{../result/cm.csv};

		\addplot[
			gray
		]
		coordinates{
			(0,0)
			(1,1)
		};
		\addplot[
			gray
		]
		coordinates{
			(0,1)
			(1,0)
		};
	\end{axis}
\end{tikzpicture}
\ref{class_legend}
\caption{
ROC points for all classifiers and dataset.
CRF-200-1 is CRF with 200 stages and 1 tree,
CRF-100-2 is CRF with 100 stages and 2 trees, and
CRF-50-4 is CRF with 50 stages and 4 trees.
}
\label{fig:rocpoints}
\end{figure*}
%%}}}

To easily compare all classifiers, all of their performance is mapped as point
in ROC space as illustrated in figure \ref{fig:rocpoints}.
On the bottom left is RF classifier, from bottom to top, RF without
resampling ($\Box$) with TPR $0.165$ and FPR $0.001$, RF on SMOTE ($\boxplus$)
with TPR $0.207$ and FPR $0.004$, and at the top is RF on LNSMOTE ($\boxtimes$)
with TPR $0.235$ and FPR $0.005$.
RF return with lowest TPR and FPR among all other classifiers.
Resampling with SMOTE on average increase the TPR by $0.25$ and FPR by 4 times
for RF.
Resampling with LNSMOTE on average increase the TPR by $0.4$ and FPR 5 times
for RF.

CRF classifier with 200 stages 1 tree (CRF-200-1) give the highest TPR, with
ROC point is on top of all classifiers.
In order from left to bottom, CRF-200-1 without resampling ($\triangle$) with
TPR $0.966$ and FPR $0.467$, CRF-200-1 on SMOTE ($\triangleleft$) in the middle
with TPR $0.979$ and FPR $0.63$, and CRF-200-1 on LNSMOTE ($\triangleright$) on
the right side with TPR $0.99$ and FPR 0.85.
CRF-200-1 will return positive sample with highest probabilites but also with
highest false-positive.
Also, the effect of SMOTE and LNSMOTE can be viewed on FPR values.
Resampling with SMOTE on average increase the TPR by $0.1$ times and $0.4$
times for FPR.
Resampling with LNSMOTE on average increase the TPR by $0.3$ times and FPR
$0.8$ times.

CRF with 100 stages and 2 tress (CRF-100-2) mapped in the top-middle of ROC
space, with marked as bullet points.
CRF-100-2 without resampling ($\medcircle$) reside at the bottom left with TPR
$0.812$ and FPR $0.24$.
CRF-100-2 on SMOTE ($\oplus$) reside in the middle, with highest AUC, and TPR
$0.903$ and FPR $0.36$.
CRF-100-2 on LNSMOTE ($\otimes$) with TPR $0.95$ and FPR $0.585$.
Resampling with SMOTE on average increase the TPR by $0.11$ times and FPR by
$0.5$ times for CRF-100-2.
Resampling with LNSMOTE on average increase the TPR by $0.17$ times and FPR by
$1.4$ times for CRF-100-2.

CRF classifiers with 50 stages and 4 trees (CRF-50-4) mapped on the middle left
of ROC space, which is marked by diamond.
CRF-50-4 without resampling ($\Diamond$) return TPR $0.607$ and FPR $0.08$.
CRF-50-4 on SMOTE ($\diamondplus$) return TPR $0.783$ and FPR $0.223$.
CRF-50-4 on LNSMOTE ($\diamondtimes$) return TPR $0.895$ and FPR $0.388$.
Resampling with SMOTE on average increase TPR by $0.3$ times and also increase
FPR by $1.75$ times for CRF-50-4.
Resampling with LNSMOTE on average increase TPR by $0.48$ times and also
increase FPR by $3.75$ times for CRF-50-4.
